Differences from our PPoPP Conference Paper \cite{KBP16}

### 2018-08-30 latex/toms/plots.tex
fixed tex compilation errors (beware, first compilation takes a very long time, but subsequent ones aren't bad)

% set options for strongscaling plot
\newcommand{\strongscalingplotoptions}{
		log basis y={2},
		log basis x={2},
		\ifliavas
			xlabel=Cores,
		\else
			xlabel=Nodes,
		\fi
		ylabel=Time (s),
		y tick label style={
	        /pgf/number format/.cd,
            	precision=4,
		},
	legend style={draw=none, cells={align=left}, nodes={scale=0.7}}
}

@@

% set options for relative error over time plot
\newcommand{\relerrplotoptions}{
	xlabel=Time (s),
	xmin=0,
	xmax=\xmax,
	domain=0:\xmax,
	\ifylabel
		ylabel=Relative Error,
		ylabel style={yshift=-.3cm},
	\fi
	\ifwider
		width=1.8in, height=2in,
	\else
		width=1.35in, height=2in,
	\fi
	y tick label style={
        /pgf/number format/.cd,
            precision=4,
	},
	legend style={draw=none, cells={align=left}, nodes={scale=0.7}}
}

@@

% set options for relative error over time plot
\newcommand{\cpuvsgpuoptions}{
	xlabel=Low Rank,
	xmin=0,
	xmax=150, 
	domain=0:150,
	\ifylabel
		ylabel=Time(s),
		ylabel style={yshift=-.3cm},
	\fi
	\ifwider
		width=2in, height=2in,
	\else
		width=1.35in, height=2in,
	\fi
	y tick label style={
        /pgf/number format/.cd,
            precision=4,
	},
	legend style={draw=none, cells={align=left}, nodes={scale=0.7}}
}

>>>>

% set options for strongscaling plot
\newcommand{\strongscalingplotoptions}{
		log basis y={2},
		log basis x={2},
		\ifliavas
			xlabel=Cores,
		\else
			xlabel=Nodes,
		\fi
		ylabel=Time (s),
		y tick label style={
	        /pgf/number format/.cd,
            	precision=4,
		% change "directory" back to tikz
                /tikz/.cd,
		},
	legend style={draw=none, cells={align=left}, nodes={scale=0.7}}
}

@@

% set options for relative error over time plot
\newcommand{\relerrplotoptions}{
	xlabel=Time (s),
	xmin=0,
	xmax=\xmax,
	domain=0:\xmax,
	\ifylabel
		ylabel=Relative Error,
		ylabel style={yshift=-.3cm},
	\fi
	\ifwider
		width=1.8in, height=2in,
	\else
		width=1.35in, height=2in,
	\fi
	y tick label style={
        /pgf/number format/.cd,
            precision=4,
            % change "directory" back to tikz
                /tikz/.cd,
	},
	legend style={draw=none, cells={align=left}, nodes={scale=0.7}}
}

@@

% set options for relative error over time plot
\newcommand{\cpuvsgpuoptions}{
	xlabel=Low Rank,
	xmin=0,
	xmax=150, 
	domain=0:150,
	\ifylabel
		ylabel=Time(s),
		ylabel style={yshift=-.3cm},
	\fi
	\ifwider
		width=2in, height=2in,
	\else
		width=1.35in, height=2in,
	\fi
	y tick label style={
        /pgf/number format/.cd,
            precision=4,
            % change "directory" back to tikz
                /tikz/.cd,
	},
	legend style={draw=none, cells={align=left}, nodes={scale=0.7}}
}
